Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-07-11 Latex/journal_v1/V5/pr.tex
code change1 and add one figure to latex

  Bandwidth & 120 KHz \\

@@

In Fig the aggregated throughput is demonstrated versus different number of UEs in each slice for these three methods. Here we assume that slices have the same priority.

>>>>

  Bandwidth & 180 KHz \\

@@

In Fig. \ref{fig:1} the aggregated throughput is demonstrated versus different number of UEs in each service for these three methods. Here we assume that services have the same priority. The figure, presented that the proposed algorithm is $35.6\%$ higher than the baseline scheme.
As the number of UEs increases in each service, the aggregated throughput initially increase, but due to interference, it will decrease from 8 UEs to 10 UEs in each service.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.45]{rate_throuput.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UE in each Service }
  \label{fig:1}
\end{figure}
